A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-06-23 src/paper.tex
'Capture of Viewer's Interaction Data' section finished

TV watching is essentially a social activity, where groups of people with a common interest share the same space and TV set for entertainment or information~\cite{Masthoff2004}. After many advances in technologies for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume. In this scenario, the data generated by viewers' interactions can provide valuable information to improve TV services, especially when data comes from millions of viewers~\cite{Teixeira2010}.

@@

The interactions between viewers and TV can be classified as implicit and explicit. Implicit interactions are part of the natural actions of watching TV e.g., changing channels and adjust sound volume. In explicit interactions, viewers contribute by actively performing actions that are not usual in the their experience from conventional TV. Such actions include among other things, evaluating audio-visual content, commenting and sharing opinion about a given content through iTV applications. Both kinds of interaction are important for services that rely on audience generated data, e.g., content personalization and targeted advertising.

@@

>>>>

TV watching is essentially a social activity, where groups of people with a common interest share the same space and TV set for entertainment or information~\cite{Masthoff2004}. After many advances in technologies for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume. In this scenario, .

@@

The interactions between viewers and TV can be classified as implicit and explicit. Implicit interactions are part of the natural actions of watching TV e.g., changing channels and adjust sound volume. In explicit interactions, viewers contribute by actively performing actions that are not usual in the their experience from conventional TV. Such actions include among other things, evaluating audio-visual content, commenting and sharing opinion about a given content through iTV applications. Both kinds of interaction are important for services that rely on audience generated data, e.g., content personalization, targeted advertising or content improvement.

 Some researchers proposed mechanisms to capture viewers' interactions in TV environments~\cite{Teixeira2010,Basilio2013,DosSantos2013}. Teixeira~\emph{et~al.}~\cite{Teixeira2010} described an infrastructure to capture both implicit and explicit interactions that are performed by means of a conventional remote control. The remote control events are recorded in XML format using elements to describe contextual information, implicit and explicit interactions. Basílio~\emph{et~al.}~\cite{Basilio2013} described two methods for capturing viewers interactions: (1) one using a middleware extension, which adds new functionalities to an existing standard; and (2) another one using applications that are added to the broadcaster data stream, which requires no changes in the middleware.

 Another research study conduced by Santos and Bianchini~\cite{DosSantos2013}, described a advertising system for interactive TV, which uses viewers interactions in order to generate targeted advertising. Basically, the described system implicitly captures metadata (e.g., the category of a TV program) information when interactions take place.

 The data generated by viewers' interactions can provide valuable information to improve TV personalization, especially when data comes from millions of viewers. For instance, viewers can change quickly the channel when a TV program loses their interest. Knowing when the channel change occurs can help producers to improve the content in order to increase viewers interest.

@@

\cite{Hwang2007}
